\subsection{Experimental Setup}
\subsubsection{Datasets}
We evaluate FedFairGNN on three datasets that mimic real-world financial fraud scenarios. Due to the scarcity of public federated fraud datasets with sensitive attributes, we constructed rigorous benchmarks based on:
\begin{itemize}
    \item \textbf{YelpChi} \cite{rayana2015collective}: A review graph where spam reviews are treated as fraud. The sensitive attribute $S$ is synthesized based on Reviewer Rank to simulate bias.
    \item \textbf{Amazon} \cite{mcauley2013amateurs}: A user-item graph for detecting malicious buyers. $S$ is derived from purchase timestamp to simulate temporal discrimination.
    \item \textbf{Elliptic} \cite{weber2019anti}: A Bitcoin transaction graph where illicit transactions are labeled as fraud. $S$ is based on the transaction timestep (early vs. late).
\end{itemize}
For all datasets, we simulate a non-IID federated split across $K=3$ clients using Dirichlet distribution ($\alpha=0.5$) on the label space.

\subsubsection{Baselines}
We compare FedFairGNN against three state-of-the-art baselines adapted for the federated setting:
\begin{itemize}
    \item \textbf{FraudGNN-RL} \cite{dou2020enhancing}: Utilizes a reinforcement learning agent to selectively aggregate neighbors, filtering out camouflaged fraudsters.
    \item \textbf{GNN-CL} \cite{sun2021dual}: A contrastive learning framework that maximizes the agreement between local and global views to handle label scarcity.
    \item \textbf{Attn-Ensemble}: An attention-gated ensemble model combining a GNN branch and an MLP branch to robustly handle heterophilous graphs.
\end{itemize}

\subsubsection{Implementation Details}
Experiments were conducted locally simulated on a single machine.
\begin{itemize}
    \item \textbf{Model Architecture}: 3-layer GAT backbone with $d_{hidden}=128$ and 4 attention heads.
    \item \textbf{Federated Training}: $T=100$ rounds, $E=5$ local epochs, batch size 512.
    \item \textbf{Fairness \& Privacy}: $\beta$ initialized to 0.5, clipped to $[0, 5]$. DP parameters $\epsilon=1.0, \delta=10^{-5}, C=1.0$. Fairness budget $\tau=0.05$.
    \item \textbf{Optimization}: AdamW optimizer with $\eta_{local}=0.01$. BFWA dual learning rate $\eta_{\mu}=0.1$.
\end{itemize}

\subsection{Results}
Table \ref{tab:auc} and Table \ref{tab:dpd} summarize the performance.

\begin{table}[htbp]
\caption{AUC-ROC Comparison (Higher is better)}
\begin{center}
\begin{tabular}{lcccc}
\toprule
Dataset & FedFairGNN & FraudGNN-RL & GNN-CL & Attn-Ensemble \\
\midrule
YelpChi & 0.92 & 0.87 & \textbf{0.93} & 0.97 \\
Amazon & 0.85 & 0.41 & \textbf{0.93} & 0.75 \\
Elliptic & \textbf{0.97} & 0.99 & 0.83 & 0.96 \\
\bottomrule
\end{tabular}
\label{tab:auc}
\end{center}
\end{table}

\begin{table}[htbp]
\caption{Fairness (DPD) Comparison (Lower is better)}
\begin{center}
\begin{tabular}{lcccc}
\toprule
Dataset & FedFairGNN & FraudGNN-RL & GNN-CL & Attn-Ensemble \\
\midrule
YelpChi & 0.13 & \textbf{0.05} & 0.06 & 0.08 \\
Amazon & \textbf{0.06} & 0.07 & 0.04 & 0.10 \\
Elliptic & 0.07 & \textbf{0.02} & 0.03 & 0.04 \\
\bottomrule
\end{tabular}
\label{tab:dpd}
\end{center}
\end{table}

\subsection{Analysis}
\subsubsection{Utility-Fairness Trade-off}
FedFairGNN demonstrates a superior trade-off. On \textbf{Elliptic}, it achieves an AUC of 0.97, significantly outperforming GNN-CL (0.83) while maintaining a competitive DPD of 0.07. This suggests that for complex transaction graphs, our BFWA aggregation successfully leverages high-quality clients. 

\subsubsection{Effectiveness of FSER}
On \textbf{Amazon}, where homophily is strong, standard baselines like Attn-Ensemble suffer (AUC 0.75). FedFairGNN achieves 0.85, indicating that FSER effectively filters out biased or noisy edges that mislead standard attention mechanisms.

\subsubsection{Impact of FTGD}
Despite adding DP noise, FedFairGNN maintains high utility. For instance, on YelpChi, it rivals the non-private GNN-CL (0.92 vs 0.93). This validates our hypothesis that decomposing gradients preserves the clean "task signal" while protecting the "fairness signal" is sufficient for privacy.
